% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2010 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Fonts
\usepackage[T1]{fontenc}
%\usepackage[urw-garamond]{mathdesign}

% Set your name here
\def\name{Dan Leyzberg}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {computer science, robotics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.5\textwidth}
  \textit{Mailing Address:} \\
  420 Temple St., Apt. 501\\
  New Haven, CT 06511
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \textit{Phone:} (732) 642-8550 \\
  \textit{E-mail:} dan.leyzberg@yale.edu \\
  \textit{Homepage:} \href{http://www.danleyzberg.com}{danleyzberg.com}
\end{minipage}

\section*{Education}

\begin{itemize}
  \item Ph.D. Computer Science, Yale University, 2014. \textbf{(Expected)}
    \begin{itemize}
    \item \textit{Dissertation:}
      Assessing Individual Learning Differences for Robot Tutors
    \item \textit{Committee:}
      Brian Scassellati, Dana Angluin,
      Drew McDermott, and Andrea Thomaz. \textbf{(In Progress)}
    \end{itemize}
  \item M.S. Computer Science, Yale University, 2009,
  \item B.S. Computer Science and Mathematics (Dual), \textit{Summa Cum Laude},
    \begin{itemize}
    \item Rensselaer Polytechnic Institute, 2007.
    \end{itemize}
\end{itemize}

\section*{Teaching Experience}

\subsection*{Hamden Hall Country Day School}
\begin{itemize}
\item AP Computer Science. Teacher. 2008-2009, 2009-2010, 2010-2011, 2011-2012.
\item Computer Science Principles. Teacher. 2009-2010, 2010-2011, 2011-2012, 2012-2013.
\\ \\ {\it Responsible for course content, syllabus, lectures, homework, tests, and grading.}
\end{itemize}

\subsection*{Hamden Hall Country Day School Summer Academy}
\begin{itemize}
\item Introduction to Robotics. Teacher. Summer 2011, Summer 2012.
\\ \\ {\it Responsible for course content, syllabus, and lectures.}
\end{itemize}

\subsection*{Yale University}
\begin{itemize}
\item Introduction to Programming, Fall 2010. Teaching Assistant for \href{http://cs-www.cs.yale.edu/homes/dvm/}{Prof. Drew McDermott}.
\item Introduction to Computer Science, Spring 2010. Teaching Assistant for \href{http://graphics.cs.yale.edu/holly/}{Prof. Holly Rushmeier}.
\item Artificial Intelligence, Fall 2009. Teaching Assistant for Prof. \href{http://cs-www.cs.yale.edu/homes/scaz/}{Brian Scassellati}.
\\ \\ {\it Responsible for office hours, grading, and review sessions.}
\end{itemize}

\subsection*{Rensselaer Polytechnic Institute}
\begin{itemize}
\item Data Structures \& Algorithms, Spring 2006. Teaching Assistant for \href{http://www.cs.rpi.edu/~magdon/}{Prof. Malik Magdon-Ismail}.
\\ \\ {\it Responsible for one-on-one office hours.}
\end{itemize}

\section*{Research Experience}

\subsection*{Yale University, Department of Computer Science}
\begin{itemize}
\item Research Assistant, Fall 2007--Present. \\
\textbf{Advisor:} \href{http://http://cs-www.cs.yale.edu/homes/scaz/}{Prof. Brian Scassellati}. \\
Member of the Social Robotics Lab.
\end{itemize}

\subsection*{Rensselaer Polytechnic Institute, Department of Computer Science}
\begin{itemize}
\item Undergraduate Research Assistant, Fall 2005--Spring 2007. \\
\textbf{Advisors:} \href{http://www.cs.rpi.edu/~goldberg/}{Prof. Mark Goldberg}, \href{http://www.cs.rpi.edu/~magdon/}{Prof. Malik Magdon-Ismail}, and \href{http://www.cs.rpi.edu/~hollingd}{Prof. Dave Hollinger}. \\
Theory research; developed novel algorithm to find minimum spanning trees for sparse random graphs.
\end{itemize}


\section*{Publications}
\subsection*{Journal Articles}
\begin{itemize}
\item E. S. Kim, L. D. Berkovits, E. P. Bernier, D. Leyzberg, F. Shic, R. Paul, and B. Scassellati. {\bf Social Robots as Embedded Reinforcers of Social Behavior in Children with Autism}. Journal of Autism and Developmental Disorders, 2012.
\end{itemize}

\subsection*{Conference Papers}
\begin{itemize}
\item D. Leyzberg, S. Spaulding, M. Toneva, and B. Scassellati. (2012). {\bf The Physical Presence of a Robot Tutor Increases Cognitive Learning Gains}. In: N. Miyake, D. Peebles, and R. P. Cooper (eds.), Proceedings of the 34th Annual Conference of the Cognitive Science Society (CogSci 2012), 1882-1887. Austin, TX: Cognitive Science Society. Sapporo, Japan, August 1-4.
\item D. Leyzberg, E. Avrunin, J. Liu, and B. Scassellati. (2011) {\bf Robots That Express Emotion Elicit Better Human Teaching}. In Proceedings of the 6th ACM/IEEE International Conference on Human Robot Interaction (HRI '11).
\item E. S. Kim, D. Leyzberg, K. M. Tsui, and B. Scassellati. (2009) {\bf How People Talk When Teaching a Robot}. In Proceedings of the 4th ACM/IEEE International Conference on Human Robot Interaction (HRI '09).
\end{itemize}

\section*{Talks \& Panels}
\begin{itemize}
	\item Panel Session on Nifty Assignments: Asteroids Arcade Game Assignment \\
	39nd ACM Technical Symposium on Computer Science Education (SIGCSE) 2008, Portland, OR.
\end{itemize}

\section*{Industry}
\begin{itemize}
	\item UBS Financial Inc., Quality Assurance Internship. Summer 2005.
\end{itemize}

\section*{Professional Activities}

\begin{itemize}
\item Reviewer for:
  \textit{Epigentic Robots 2010},
  \textit{Human-Robot Interaction 2009, 2010, 2011, 2012, 2013, 2014}.
\item Departmental Service: Graduate Teaching Liaison, 2009-10.
\end{itemize}

%\section*{Honors, Awards, \& Fellowships}
%
%\begin{itemize}
%\item Summer Research Fellowship, Duke University, 2007, 2008.
%\item Institute on Computational Economics Fellow, University of Chicago, 2006.
%\item Outstanding Teaching Assistant Award, Duke University, 2006.
%\item Undergraduate Research Award, North Carolina State University, 2004.
%% \item Omicron Delta Epsilon, International Economics Honor Society, 2004.
%\item Phi Beta Kappa, Zeta of North Carolina, 2003.
%% \item Pi Mu Epsilon, National Mathematics Honor Society, 2003.
%\item NSF Research Experiences for Undergraduates, Colorado School of Mines, 2002.
%% \item Phi Kappa Phi, 2002.
%% \item Golden Key International Honour Society, 2002.
%% \item Dean's List, North Carolina State University, 2000--2004.
%\end{itemize}
%%
%\section*{Conferences and Workshops Attended}
%
%\begin{itemize}
%\item AEA/ASSA Annual Meetings,
%  Denver, CO, January 6--10, 2011.
%\item 20th Annual Meetings of the Midwest Econometrics Group,
%  Washington University,
%  October 1--2, 2010.
%\item AEA/ASSA Annual Meetings,
%  Atlanta, GA, January 3--5, 2010.
%\item Triangle Econometrics Conference,
%  Research Triangle Park, NC,
%  December 4, 2009.
%\item Cowles Foundation Conference, Applications of Structural Microeconomics,
%  Yale University,
%  June 24--25, 2009.
%\item ERID Conference on Identification,
%  Duke University,
%  October 3--4, 2008.
%\item North American Summer Meetings of the Econometric Society,
%  Duke University,
%  June 21--24, 2007.
%\item Institute on Computational Economics,
%  Argonne National Laboratory,
%  July 17--21, 2006.
%\item SIAM Conference on Applied Linear Algebra,
%  The College of William \& Mary,
%  July 15--19, 2003.
%\end{itemize}
%
%\section*{Miscellaneous}
%
%\begin{itemize}
%\item \textit{Security Clearance:} Special Sworn Status, U.S. Census Bureau.
%\end{itemize}

\medskip

% Footer
%\begin{center}
%  \begin{small}
%    Last updated: \today
%  \end{small}
%\end{center}

\end{document}
